Technical Report

### 2018-01-07 fully-abstract-comp/technical-report.tex
Typo in execCond and correction to P-relation: pair of data now trivially okay. World needs to be split up
Added definition for terminating computation
Remove obsolete comment.

@@

\dominique{4-12-2017: $e_\stk$ is no longer stored in $\ms_{\stk,\priv}$ in updated call implementation.}
\lau{12-12-2017: Correct. Please feel free to correct these things.}

@@

\[
  \lrp(W) = \left\{
    \npair{ \overline{\stpair[.]{c}{c'}} } \middle| 
    \begin{array}{l}
      \text{for $\stpair[.]{c}{c'} \in \overline{\stpair[.]{c}{c'}}$} \\
      \src{\baddr} = \pi_\baddr(\src{c}) \wedge \src{\eaddr} = \pi_\eaddr(\src{c}) \wedge 
      \baddr = \pi_\baddr(c) \wedge \eaddr = \pi_\eaddr(c) \wedge \\
      \src{\lin} = \pi_\lin(\src{c}) = \pi_\lin(c) \\
      \quad \exists r \in \addressable{l,W} \ldotp\\
      \qquad \forall \npair{\stpair{\ms}{\ms}} \in W(r).H \; W(r).s \; \xi^{-1}(W)  \ldotp \\
      \qquad \quad \dom(\src{\ms_S}) \subseteq [\src{\baddr},\src{\eaddr}] \wedge \dom(\ms_T) \subseteq [\baddr,\eaddr]      
    \end{array}
  \right\}
\]

@@

\[
  \execCond{\lin,W} = \left\{ \npair{(S_\perm,\baddr,\eaddr)} \middle|
    \begin{array}{l}
      \forall n' < n, W' \privft W, \perm \in S_\perm, \aaddr \in [\baddr,\eaddr] \ldotp\\
      \quad \forall W'', c_{d,S},c_{d,T} \ldotp \npair[n']{\stpair[.]{c_{d,S}}{c_{d,T}}} \in \lrv(W'') \wedge \\
      \qquad \npair[n']{[\stpair[.]{((\perm,lin),\baddr,\eaddr,\aaddr)}{((\perm,lin),\baddr,\eaddr,\aaddr)},\stpair[.]{c_{d,S}}{c_{d,T}}]} \in \lrp(W' \oplus W'') \Rightarrow \\
      \quad \qquad \npair[n']{\stpair[.]{((\perm,lin),\baddr,\eaddr,\aaddr)}{((\perm,lin),\baddr,\eaddr,\aaddr)},\stpair[.]{c_{d,S}}{c_{d,T}}} \in \lre(W' \oplus W'')
    \end{array}
    \right\}
\]

@@

\begin{theorem}[FTLR]
  \label{thm:ftlr}
  \[
    \begin{array}{l}
      \forall n,W,W_D,W_C,\perm_C,\perm_D,\lin_C,\lin_D,\baddr_C,\baddr_D,\eaddr_C,\eaddr_D,\aaddr_C,\aaddr_D \ldotp \\
      \quad \left(
      \begin{array}{l}
        W = W_D \oplus W_C \wedge \\
        \perm_D \in \readAllowed{} \Rightarrow \npair{(\baddr_D,\eaddr_D)} \in \readCond{\lin_D,W_D} \wedge\\
        \perm_D \in \writeAllowed{} \Rightarrow\npair{(\baddr_D,\eaddr_D)} \in \writeCond{\lin_D,W_D} \wedge\\
        \perm_D \notin \{\rwx,\rx\} \wedge \\
        \perm_C = \rx \wedge\\
        \npair{(\{\rx\},\baddr_C,\eaddr_C)} \in \execCond{\lin_C,W_C}
      \end{array}
      \right)\\
      \quad\Rightarrow 
      \npair{\arraycolsep=0pt\array{l}((\perm_C,\lin_C),\baddr_C,\eaddr_C,\aaddr_C),((\perm_D,\lin_D),\baddr_D,\eaddr_D,\aaddr_D),\\
                      ((\perm_C,\lin_C),\baddr_C,\eaddr_C,\aaddr_C),((\perm_D,\lin_D),\baddr_D,\eaddr_D,\aaddr_D)\endarray} \in \lre(W)

>>>>

\paragraph{Termination computations}
We use the following notation to write that a configuration $\Phi$ successfully terminates:
\[
  \Phi\term[i] \defeq \Phi \nstep[i] \halted
\]
if we just know $\Phi$ terminates in some number of steps, then we write
\[
  \Phi\term \defeq \exists i \ldotp \term[i]
\]

@@

@@

\[
  \lrp(W) =
    \left\{
    \npair{ [\stpair[.]{c_1}{c'_1}, \dots, \stpair[.]{c_k}{c'_k}] } \middle| 
    \begin{array}{l}
      \exists S : \{1,\dots,k\} \fun \World \ldotp \\
      \quad W = \bigoplus_{i\in\{1,\dots,k\}} S(i)\wedge \\
      \quad\text{for $i \in \{1,\dots,k\}$} \\
      \qquad\stpair[.]{c_i}{c'_i} \in \ints \times \ints \vee \\
      \qquad\src{\baddr} = \pi_\baddr(\src{c_i}) \wedge \src{\eaddr} = \pi_\eaddr(\src{c_i}) \wedge \\
      \qquad\baddr = \pi_\baddr(c_i') \wedge \eaddr = \pi_\eaddr(c_i') \wedge \\
      \qquad\src{\lin} = \pi_\lin(\src{c_i}) = \pi_\lin(c_i') \wedge \\
      \qquad \exists r \in \addressable{l,S(i)} \ldotp\\
      \qquad \quad \forall \npair{\stpair{\ms}{\ms}} \in S(i)(r).H \; S(i)(r).s \; \xi^{-1}(S(i))  \ldotp \\
      \qquad \qquad \dom(\src{\ms_S}) \subseteq [\src{\baddr},\src{\eaddr}] \wedge \dom(\ms_T) \subseteq [\baddr,\eaddr]      
    \end{array}
  \right\}
\]

@@

\[
  \execCond{\lin,W} = \left\{ \npair{(S_\perm,\baddr,\eaddr)} \middle|
    \begin{array}{l}
      \forall n' < n, W' \privft W, \perm \in S_\perm, \aaddr \in [\baddr,\eaddr] \ldotp\\
      \quad \forall W'', c_{d,S},c_{d,T} \ldotp \npair[n']{\stpair[.]{c_{d,S}}{c_{d,T}}} \in \lrv(W'') \wedge \\
      \qquad \npair[n']{[\stpair[.]{((\perm,\lin),\baddr,\eaddr,\aaddr)}{((\perm,\lin),\baddr,\eaddr,\aaddr)},\stpair[.]{c_{d,S}}{c_{d,T}}]} \in \lrp(W' \oplus W'') \Rightarrow \\
      \quad \qquad \npair[n']{\stpair[.]{((\perm,\lin),\baddr,\eaddr,\aaddr)}{((\perm,\lin),\baddr,\eaddr,\aaddr)},\stpair[.]{c_{d,S}}{c_{d,T}}} \in \lre(W' \oplus W'')
    \end{array}
    \right\}
\]

@@

\begin{theorem}[FTLR]
  \label{thm:ftlr}
  \[
    \begin{array}{l}
      \forall n,W,W_D,W_C,\perm_C,\perm_D,\lin_C,\lin_D,\baddr_C,\baddr_D,\eaddr_C,\eaddr_D,\aaddr_C,\aaddr_D \ldotp \\
      \quad \left(
      \begin{array}{l}
        W = W_D \oplus W_C \wedge \\
        \perm_D \in \readAllowed{} \Rightarrow \npair{(\baddr_D,\eaddr_D)} \in \readCond{\lin_D,W_D} \wedge\\
        \perm_D \in \writeAllowed{} \Rightarrow\npair{(\baddr_D,\eaddr_D)} \in \writeCond{\lin_D,W_D} \wedge\\
        \perm_D \notin \{\rwx,\rx\} \wedge \\
        \perm_C = \rx \wedge\\
        \npair{(\baddr_C,\eaddr_C)} \in \readCond{\lin_C,W_C}
      \end{array}
      \right)\\
      \quad\Rightarrow 
      \npair{\arraycolsep=0pt\array{l}((\perm_C,\lin_C),\baddr_C,\eaddr_C,\aaddr_C),((\perm_D,\lin_D),\baddr_D,\eaddr_D,\aaddr_D),\\
                      ((\perm_C,\lin_C),\baddr_C,\eaddr_C,\aaddr_C),((\perm_D,\lin_D),\baddr_D,\eaddr_D,\aaddr_D)\endarray} \in \lre(W)
